\propertitle

### 2019-04-18 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-04-18T16:17:13+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

These premisses may represent either actual knowledge or just some
hypotheses whose consequences we want to explore. They can be
\setlength{\intextsep}{0.5ex}% with wrapfigure
\begin{wrapfigure}{l}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme1.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
assigned at different depths of the logical analysis of our inference
problem, and assignments at different depths can turn out to be
equivalent.

We can for example assign probabilistic premisses at a very deep
level, as schematically illustrated on the left. They will determine the
probabilities of statements at all higher levels, including the statements
we're ultimately interested in.

Or we can assign probabilistic premisses at
a level of intermediate
\begin{wrapfigure}{r}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme2.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
depth, as schematically illustrated on the right. In this case they will
determine the probabilities of statements at all higher level, and partly
constrain the probabilities of statements at deeper levels.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-04-18T21:40:56+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation constraints%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample constraints}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

These premisses may represent either actual knowledge or just
\setlength{\intextsep}{0.5ex}% with wrapfigure
\begin{wrapfigure}{l}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme1.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
some hypotheses whose consequences we want to explore. They can be assigned
at different depths of the logical analysis of our inference problem.

We can for example assign probabilistic premisses at a very deep
level, as schematically illustrated on the left. They determine the
probabilities of statements at all higher levels, including the statements
we're ultimately interested in.

\begin{wrapfigure}{r}{0.33\linewidth}% with wrapfigure
\centering\includegraphics[width=\linewidth]{statements_scheme2b.pdf}%\\
%\caption{caption}\label{fig:comparison_a5}
\end{wrapfigure}% statements_scheme.svg statements_scheme2.svg
Or we can assign probabilistic premisses at a level of intermediate depth,
as schematically illustrated on the right. In this case they determine the
probabilities of statements at all higher levels, and partly constrain
the probabilities of statements at deeper levels.

The choice of the logical level at which to assign the premisses depends on
many factors: on the difficulty of assessing our state of knowledge at
particular levels, on the cost of the ensuing calculations, and especially
on the general purpose of our inference. But two assignments of premisses at
different levels can still turn out to be completely equivalent for the
probabilities of the statements of interest.

The maximum-entropy principle was proposed first by Jaynes
\parentext{\cite*{jaynes1957,jaynes1963,jaynes1994_r2003};
  \cite{sivia1996_r2006,hobsonetal1973}} as a way of assigning probability
premisses at a level of intermediate depth -- this point is made
especially clear in \textcite[\sect~11.1]{jaynes1994_r2003}.
